Convergence rate of MAP estimates \\ for the exponential family

### 2021-05-11 main.tex
Start typing proof of integral

As for the MAP, we did not manage to get an asymptotically tight upper bound. Nevertheless, using inequality~\eqref{eq:log_bound}, we did get an interesting upper bound. 
To start, let us recall that the MAP of $\cN(0,\mu_*)$ is $\hat \mu_n = \frac{n_0 \mu_0 + \sum_i X_i^2}{n_0 + n}$.
Its expectation is simply $\mu_n= \frac{n_0 \mu_0 + n \mu^*}{n_0 + n}$.
We now present a lemma on its expected inverse.
\begin{lemma}[Expected MAP natural parameter]
	The expectation of the natural parameter of the MAP of $\cN(0,\mu_*)$ is bounded as
	\begin{align}
		\frac{\mu^*}{\mu_n}
		\leq \expect{\frac{\mu^*}{\MAPm}} 
		= \expect{\frac{\MAPt}{\natp^*}} 
		\leq \frac{1}{\frac{\mu_n}{\mu^*} - \frac{2}{n+n_0}} \; .
	\end{align}
\end{lemma}
Using this lemma, along with~\eqref{eq:log_bound}, we get the following result.
\begin{theorem}[MAP Upper Bound]
 The expected suboptimality of the MAP of $\cN(0,\mu^*)$ with prior hyper-parameters $(n_0,\mu_0)$ is 
\begin{equation}
	\expect{\bregmanconj( \mu_*; \hat \mu_n^\text{MAP})}
	\leq \begin{cases}
		\bregmanconj( \mu_*; \mu_0) \ \text{ if } \ n=0, \\
		\frac{1+n_0}{4} e^{\half[a]} \sqrt{\frac{2 \pi}{a}} \mathrm{erfc}(\sqrt{\half[a]})  - \half  + \frac{a - n_0}{2(1+n_0)} \ \text{if}\ n=1,\\
		\frac{1}{a+n-2} + \frac{\half(1 - \frac{\mu_0}{\mu^*})^2}{(\frac{\mu_0}{\mu^*}+\frac{n-2}{n_0})(1 + \frac{n}{n_0} )} if n\geq 2 \ \text{and}\ a=n_0 \frac{\mu_0}{\mu^*} >0
	\end{cases}
\end{equation}
\end{theorem}

\begin{proof}
	Wolfram finds no closed form for $\expect{\log\frac{\MAPm}{\mu^*}}$ but it does for $\expect{\frac{\mu^*}{\MAPm}} = \expect{\frac{\MAPt}{\natp^*}}$. 
	To start, let us plug in the definition of $\MAPm$
	\begin{align}
		\expect{\frac{\mu^*}{\MAPm}} 
		= \expect{\frac{\MAPt}{\natp^*}} 
		&= expect{\frac{(n_0+n) \mu^*}{n_0 \mu_0 + \sum_i X_i^2}}  \\
		&= (n_0 + n) \expect{\inv{n_0 \frac{\mu_0}{\mu^*}+ \sum_i \frac{X_i^2}{ \mu^*} }} \\
		&= (n_0 +n) \expect{\inv{a + \chi^2(n)}}
	\end{align}
	where $\chi^2(n) = \sum_i \frac{X_i^2}{ \mu^*}$ is a chi-square random variable of degree $n$ and 
	\begin{align}
			a=n_0 \frac{\mu_0}{\mu^*} \; .
	\end{align}
	This expectations is not simple to solve, but using the trick
	\begin{align}
		&\int_1^\infty e^{-\frac{zt}{2}} dt = \frac{2}{z} e^{-\half[z]} 
		\ \implies \ \inv{z} = \half e^{\half[z]} \int_1^\infty e^{-\frac{zt}{2}} dt
		\\
		\implies 
		&\inv{a+x} = \half e^{\frac{a+x}{2}} \int_1^\infty e^{- \frac{(a+x)t}{2}}dt \; ,
	\end{align} 
	we get  the formula :
	\begin{align}
		(n_0 +n) \expect{\inv{a + \chi^2(n)}}  = \half[n_0+n] e^{\frac{a}{2}} E_{\half[n]}(\half[a])
		\label{eq:wolfram_input}
	\end{align}
	where the \href{https://dlmf.nist.gov/8.19}{generalized exponential integral function} is defined as 
	\begin{align}
		E_k(z) = \int_1^\infty \frac{e^{-z t} }{t^k} dt \; .
	\end{align}
	Now our goal is to bound this function with simpler functions.
	Fortunately, mathematicians have been working on these integrals for decades.
	When $n=2$, we have the simple exponential integral function which \href{https://dlmf.nist.gov/6.8\#E1}{verifies the bound}
	\begin{align}
		\half \log(1 + \frac{2}{x}) 
		\leq e^x E_1(x) 
		\leq \log(1+\inv{x}) \leq \inv{x} \; .
	\end{align}
	or 
	\begin{align}
		E_{\half[1]}(\half[a]) = \sqrt{\frac{a}{2\pi}}
	\end{align}
	For larger $n$, we have \href{https://dlmf.nist.gov/8.19\#E21}{the general bound}
	\begin{align}
		\inv{x+k}
		\leq e^x E_k(x) 
		\leq \inv{x + k - 1}
	\end{align}
	so that 
	\begin{align}
		\inv{a+n}
		\leq \expect{\inv{a + \chi^2(n)}}
		\leq \inv{a + n - 2}
	\end{align}
	so that
	\begin{align}
		\frac{n +n_0}{2 \mu^* (a + n)}	
		&\leq - \E[\MAPt]
		\leq \frac{n +n_0}{2 \mu^* (a + n - 2)}	\\
		\iff \inv{2 \mu_n}
		&\leq - \E[\MAPt]
		\leq \inv{2 \mu_n - \frac{4 \mu^*}{n + n_0}}	\\
		\iff \frac{\mu^*}{\mu_n}
		&\leq \expect{\frac{\mu^*}{\MAPm}} 
		\leq \frac{\mu^*}{\mu_n - \frac{2 \mu^*}{n + n_0}}  
		\label{eq:theta_expectation_bound}
	\end{align}
	because $\frac{\mu^* (a + n)}{n +n_0} = \mu_n$.
Now using the bound \eqref{eq:log_bound} on the logarithm, we get
\begin{align}
	2\expect{\bregmanconj(\mu^*; \MAPm)} 
	&\leq \expect{\frac{\mu^*}{\MAPm}}  + \expect{\frac{\MAPm}{\mu^*}} - 1 \\
	&\leq \frac{\mu^*}{\mu_n - \frac{2 \mu^*}{n + n_0}}   + \frac{\mu_n}{\mu^*} - 1 \\
	&= \frac{n_0 + n}{a +n - 2} + \frac{a+n}{n_0 + n} - 2 \\
	&= \frac{n_0 - a + 2}{a +n - 2} + \frac{a - n_0}{n_0 + n} \\
	&= \frac{2}{a+n-2} + \frac{(n_0 - a)^2}{(a+n-2)(n_0 + n)} \\
	\implies \expect{\bregmanconj(\mu^*; \MAPm)} 
	&\leq \frac{1}{a+n-2} + \frac{(n_0 - a)^2}{2(a+n-2)(n_0 + n)} \\
	&\leq \frac{1}{a+n-2} + \frac{\half(1 - \frac{\mu_0}{\mu^*})^2}{(\frac{\mu_0}{\mu^*}+\frac{n-2}{n_0})(1 + \frac{n}{n_0} )} 
\end{align}
where recall that $a=n_0\frac{\mu_0}{\mu^*}$. 
This inequality highlights a clear variance-bias decomposition, to compare with the MLE. Unfortunately it is not tight asymptotically as the inequality \eqref{eq:log_bound} is not quadratically tight around $1$. We are basically losing a factor 2 compared to $1/2n$. 
\end{proof}

@@

\section{Proofs for Gaussian Variance}
\subsection{MLE Tight Upper Bound}
	\begin{theorem}[MLE tight upper bound]
	The MLE of $\cN(0,\mu_*)$ is $\mu_n = \inv{n} \sum_i X_i^2 $.
	Its expected suboptimality is infinite when $n\leq 2$ and 
	\begin{align}
		 \expect{\bregmanconj( \mu_*; \mu_n) }
			\leq \inv{2n} +\frac{2}{n(n-2)}
	\end{align}
	otherwise. Note that this upper bound is asymptotically tight.
	\end{theorem}

	\begin{proof}
	The ratio to the optimum  $\frac{\mu_n}{\mu_*}$follows a \href{https://en.wikipedia.org/wiki/Chi-square_distribution}{Chi-square distribution} with $n$ degrees of freedom $\chi^2(n)$ divided by $n$. Its inverse $\frac{\mu_*}{ \mu_n} $ follows an \href{https://en.wikipedia.org/wiki/Inverse-chi-squared_distribution}{inverse Chi-square distribution} with expectation 
	\begin{align}
		\expect{\frac{\mu_*}{ \mu_n}  - 1} 
		= \expect{\frac{n}{\chi^2(n)} - 1} =
		\begin{cases}
			\frac{n}{n-2} -1 = \frac{2}{n-2} \ \text{ if } n>2, \\
			+\infty \  \text{ otherwise. }
		\end{cases}
	\end{align}
	There is also a closed form solution for the expected logarithm of a Chi-squared\citep{pav2015moments}
	\begin{align}
		\expect{\log \frac{\mu_n}{\mu_*}} = \psi(\half[n]) - \log(\half[n])
	\end{align}
	where $\psi$ is the \href{https://en.wikipedia.org/wiki/Digamma_function}{digamma function.}
	Consequently the suboptimality of the MLE has a closed form solution
	\begin{align}
	\expect{\bregmanconj( \mu_*; \mu_n) }
	&= \half \expect{\frac{\mu_*}{ \mu_n} - 1 + \log \left(\frac{\mu_n}{\mu_*} \right) } \\
	& =
	\begin{cases}
		\half \left ( \frac{2}{n-2} +\psi(\half[n]) - \log(\half[n]) \right )  \ \text{ if } n>2, \\
			+\infty \  \text{ otherwise. }
	\end{cases}
	\end{align}
	It is surprising that we need more than $3$ samples for the loss to have a bounded expectation. 
	It is also very pleasant that the optimal value $\mu_*$ does not appear in this rate, so that the convergence rate is independent of the actual solution.
	When the expectation is finite, we can make its formula intelligible thanks to \href{https://en.wikipedia.org/wiki/Digamma_function#Inequalities}{bounds on the digamma function}
	\begin{align}
		-\inv{x} \leq \psi(x) - \log(x) \leq -\inv{2x}	\; .
	\end{align}
	  For $n\geq 3$,
	\begin{align}
		\inv{n-2} - \inv{n}
		&\leq \expect{\bregmanconj( \mu_*; \mu_n) }
		\leq \inv{n-2} - \inv{2 n} \\
		\iff
			\frac{2}{n(n-2)}
			&\leq \expect{\bregmanconj( \mu_*; \mu_n) }
			\leq \inv{2n} +\frac{2}{n(n-2)}
	\end{align}
	so we get a $O(n^{-2})$ lower bound and a $O(n^{-1}) + O(n^{-2})$ upper bound.
	\end{proof}

	Using the \href{https://en.wikipedia.org/wiki/Digamma_function#Recurrence_formula_and_characterization}{Stirling series}, we can also get an asymptotic approximation
	\begin{align}
		\expect{\bregmanconj( \mu_*; \mu_n) }
		\in \inv{2n} + \frac{11}{6 n^2} + \frac{4}{n^2(n-2)} + O(n^{-4}) \; .
	\end{align}

@@

>>>>

As for the MAP, we did not manage to get an asymptotically tight upper bound. Nevertheless, using inequality~\eqref{eq:log_bound}, we did get an interesting upper bound. 
To start, let us recall that the MAP of $\cN(0,\mu_*)$ is $\hat \mu_n = \frac{n_0 \mu_0 + \sum_i X_i^2}{n_0 + n}$.
Its expectation is simply $\mu_n= \frac{n_0 \mu_0 + n \mu^*}{n_0 + n}$.
We now present a lemma on its expected inverse.
\begin{lemma}[Expected MAP natural parameter]
	For any $n\geq 2$, the expectation of the natural parameter of the MAP of $\cN(0,\mu_*)$ is bounded as
	\begin{align}
		\frac{\mu^*}{\mu_n}
		\leq \expect{\frac{\mu^*}{\MAPm}} 
		= \expect{\frac{\MAPt}{\natp^*}} 
		\leq \frac{1}{\frac{\mu_n}{\mu^*} - \frac{2}{n+n_0}} \; .
	\end{align}
\end{lemma}
Not that the lower bound is a simple consequence of the convexity of the inverse function. Using this lemma, along with~\eqref{eq:log_bound}, we get the following result.
\begin{theorem}[MAP Upper Bound]
 Introducing $a=n_0 \frac{\mu_0}{\mu^*}$, the expected suboptimality of the MAP of $\cN(0,\mu^*)$ with prior hyper-parameters $(n_0,\mu_0)$ is 
\begin{equation}
	\expect{\bregmanconj( \mu_*; \hat \mu_n^\text{MAP})}
	\leq \begin{cases}
		\bregmanconj( \mu_*; \mu_0) \ \text{ if } \ n=0, \\
		\bregmanconj( \mu_*; \mu_0) + \inv{a} \ \text{if}\ n=1,\\
		\frac{1}{a+n-2} + \frac{\half(1 - \frac{\mu_0}{\mu^*})^2}{(\frac{\mu_0}{\mu^*}+\frac{n-2}{n_0})(1 + \frac{n}{n_0} )} \ \text{if}\  n\geq 2 \ \text{and}\ a=n_0 \frac{\mu_0}{\mu^*} >0
	\end{cases}
\end{equation}
\end{theorem}

@@

\section{Proofs for Gaussian Variance}
\subsection{MLE Tight Upper Bound}
	\begin{theorem}[MLE tight upper bound]
	The MLE of $\cN(0,\mu_*)$ is $\mu_n = \inv{n} \sum_i X_i^2 $.
	Its expected suboptimality is infinite when $n\leq 2$ and otherwise
	\begin{align}
		 \expect{\bregmanconj( \mu_*; \mu_n) }
			\leq \inv{2n} +\frac{2}{n(n-2)} \; .
	\end{align}
	\end{theorem}

	\begin{proof}
	The ratio to the optimum  $\frac{\mu_n}{\mu_*}$follows a \href{https://en.wikipedia.org/wiki/Chi-square_distribution}{Chi-square distribution} with $n$ degrees of freedom $\chi^2(n)$ divided by $n$. Its inverse $\frac{\mu_*}{ \mu_n} $ follows an \href{https://en.wikipedia.org/wiki/Inverse-chi-squared_distribution}{inverse Chi-square distribution} with expectation 
	\begin{align}
		\expect{\frac{\mu_*}{ \mu_n}  - 1} 
		= \expect{\frac{n}{\chi^2(n)} - 1} =
		\begin{cases}
			\frac{n}{n-2} -1 = \frac{2}{n-2} \ \text{ if } n>2, \\
			+\infty \  \text{ otherwise. }
		\end{cases}
	\end{align}
	There is also a closed form solution for the expected logarithm of a Chi-squared\citep{pav2015moments}
	\begin{align}
		\expect{\log \frac{\mu_n}{\mu_*}} = \psi(\half[n]) - \log(\half[n])
	\end{align}
	where $\psi$ is the \href{https://en.wikipedia.org/wiki/Digamma_function}{digamma function.}
	Consequently the suboptimality of the MLE has a closed form solution
	\begin{align}
	\expect{\bregmanconj( \mu_*; \mu_n) }
	&= \half \expect{\frac{\mu_*}{ \mu_n} - 1 + \log \left(\frac{\mu_n}{\mu_*} \right) } \\
	& =
	\begin{cases}
		\half \left ( \frac{2}{n-2} +\psi(\half[n]) - \log(\half[n]) \right )  \ \text{ if } n>2, \\
			+\infty \  \text{ otherwise. }
	\end{cases}
	\end{align}
	It is surprising that we need more than $3$ samples for the loss to have a bounded expectation. 
	It is also very pleasant that the optimal value $\mu_*$ does not appear in this rate, so that the convergence rate is independent of the actual solution.
	When the expectation is finite, we can make its formula intelligible thanks to \href{https://en.wikipedia.org/wiki/Digamma_function#Inequalities}{bounds on the digamma function}
	\begin{align}
		-\inv{x} \leq \psi(x) - \log(x) \leq -\inv{2x}	\; .
	\end{align}
	  For $n\geq 3$,
	\begin{align}
		\inv{n-2} - \inv{n}
		&\leq \expect{\bregmanconj( \mu_*; \mu_n) }
		\leq \inv{n-2} - \inv{2 n} \\
		\iff
			\frac{2}{n(n-2)}
			&\leq \expect{\bregmanconj( \mu_*; \mu_n) }
			\leq \inv{2n} +\frac{2}{n(n-2)}
	\end{align}
	so we get a $O(n^{-2})$ lower bound and a $O(n^{-1}) + O(n^{-2})$ upper bound.
	\end{proof}
	Using the \href{https://en.wikipedia.org/wiki/Digamma_function#Recurrence_formula_and_characterization}{Stirling series}, we can also get an asymptotic approximation
	\begin{align}
		\expect{\bregmanconj( \mu_*; \mu_n) }
		\in \inv{2n} + \frac{11}{6 n^2} + \frac{4}{n^2(n-2)} + O(n^{-4}) \; .
	\end{align}

@@

\subsection{Expected MAP Natural Parameter}
\begin{lemma}[Expected MAP natural parameter]
	The expectation of the natural parameter of the MAP of $\cN(0,\mu_*)$ is bounded as
	\begin{align}
		\frac{\mu^*}{\mu_n}
		\leq \expect{\frac{\mu^*}{\MAPm}} 
		= \expect{\frac{\MAPt}{\natp^*}} 
		\leq \frac{1}{\frac{\mu_n}{\mu^*} - \frac{2}{n+n_0}} \; .
	\end{align}
\end{lemma}

\begin{proof}
	To start, let us plug in the definition of $\MAPm$
	\begin{align}
		\expect{\frac{\mu^*}{\MAPm}} 
		= \expect{\frac{\MAPt}{\natp^*}} 
		&= \expect{\frac{(n_0+n) \mu^*}{n_0 \mu_0 + \sum_i X_i^2}}  \\
		&= (n_0 + n) \expect{\inv{n_0 \frac{\mu_0}{\mu^*}+ \sum_i \frac{X_i^2}{ \mu^*} }} \\
		&= (n_0 +n) \expect{\inv{a + \chi^2(n)}}
	\end{align}
	where $\chi^2(n) = \sum_i \frac{X_i^2}{ \mu^*}$ is a chi-square random variable of degree $n$ and 
	\begin{align}
			a=n_0 \frac{\mu_0}{\mu^*} \; .
	\end{align}
	We reformulate this expectation with the trick
	\begin{align}
		&\int_1^\infty e^{-\frac{zt}{2}} dt = \frac{2}{z} e^{-\half[z]} \\
		\implies &\inv{z} = \half e^{\half[z]} \int_1^\infty e^{-\frac{zt}{2}} dt \\
		\implies &\inv{a+x} = \half e^{\frac{a+x}{2}} \int_1^\infty e^{- \frac{(a+x)t}{2}}dt \; ,
	\end{align} 
	to get two integrals instead of one
	\begin{align}
		2^{\half[n]}\Gamma(\half[n]) \expect{\inv{a + \chi^2(n)}}  
		&= \int_0^\infty \frac{x^{\frac{n}{2}-1}e^{-\half[x]} }{a+x} dx \\
		&= \int_0^\infty dx x^{\frac{n}{2}-1}e^{-\half[x]} \half e^{\half[a+x]} \int_1^\infty  dt  e^{-\half[(a+x)t]}  \\
		&= \half e^{\half[a]} \int_1^\infty dt \ e^{-\half[a t]}   \int_0^\infty dx \  x^{\frac{n}{2}-1} e^{-\half[x t]}  \; ,
	\end{align}
	where we used Fubini to switch integrals, without further justification.
	Now with the change of variable $x = 2\frac{y}{t}$, eg $dx = 2\frac{dy}{t}$, the inner integral becomes \TODO{finish}.
	we get  the formula :
	\begin{align}
		(n_0 +n) \expect{\inv{a + \chi^2(n)}}  = \half[n_0+n] e^{\frac{a}{2}} E_{\half[n]}(\half[a])
		\label{eq:wolfram_input}
	\end{align}
	where the \href{https://dlmf.nist.gov/8.19}{generalized exponential integral function} is defined as 
	\begin{align}
		E_k(z) = \int_1^\infty \frac{e^{-z t} }{t^k} dt \; .
	\end{align}
	Now our goal is to bound this function with simpler functions.
	Fortunately, mathematicians have been working on these integrals for decades.
	When $n=2$, we have the simple exponential integral function which \href{https://dlmf.nist.gov/6.8\#E1}{verifies the bound}
	\begin{align}
		\half \log(1 + \frac{2}{x}) 
		\leq e^x E_1(x) 
		\leq \log(1+\inv{x}) \leq \inv{x} \; .
	\end{align}
	When $n=1$, the integral can be written with the complementary error function
	\begin{align}
		E_{\half[1]}(\half[a]) = \sqrt{\frac{2\pi}{a}} \mathrm{erfc}(\sqrt{\half[a]}) \; .
	\end{align}
	For $n \geq 2$, eg $k\geq 1$, we have \href{https://dlmf.nist.gov/8.19\#E21}{the general bound}
	\begin{align}
		\inv{x+k}
		\leq e^x E_k(x) 
		\leq \inv{x + k - 1}
	\end{align}
	so that 
	\begin{align}
		\inv{a+n}
		&\leq \expect{\inv{a + \chi^2(n)}}
		\leq \inv{a + n - 2} \\
		\iff \frac{n +n_0}{a + n}	
		&\leq  \expect{\frac{\mu^*}{\MAPm}} 
		\leq \frac{n +n_0}{a + n - 2}	\\
		\iff \frac{\mu^*}{\mu_n}
		&\leq \expect{\frac{\mu^*}{\MAPm}} 
		\leq \frac{1}{\frac{\mu_n}{\mu^*} - \frac{2}{n + n_0}}  
		\label{eq:theta_expectation_bound}
	\end{align}
	where we used $\frac{a + n}{n +n_0} = \mu_n$.
\end{proof}

\subsection{MAP Upper Bound}
\begin{theorem}[MAP Upper Bound]
 The expected suboptimality of the MAP of $\cN(0,\mu^*)$ with prior hyper-parameters $(n_0,\mu_0)$ is 
\begin{equation}
	\expect{\bregmanconj( \mu_*; \hat \mu_n^\text{MAP})}
	\leq \begin{cases}
		\bregmanconj( \mu_*; \mu_0) \ \text{ if } \ n=0, \\
		\bregmanconj( \mu_*; \mu_0) +\inv{a} \ \text{if}\ n=1,\\
		\frac{1}{a+n-2} + \frac{\half(1 - \frac{\mu_0}{\mu^*})^2}{(\frac{\mu_0}{\mu^*}+\frac{n-2}{n_0})(1 + \frac{n}{n_0} )} if n\geq 2 \ \text{and}\ a=n_0 \frac{\mu_0}{\mu^*} >0
	\end{cases}
\end{equation}
\end{theorem}

$\frac{1+n_0}{4} e^{\half[a]} \sqrt{\frac{2 \pi}{a}} \mathrm{erfc}(\sqrt{\half[a]})  - \half  + \frac{a - n_0}{2(1+n_0)} $

\begin{proof}
		Wolfram finds no closed form for $\expect{\log\frac{\MAPm}{\mu^*}}$ so we focus solely on the simpler upper bound given Now using the bound \eqref{eq:log_bound} on the logarithm, we get
\begin{align}
	2\expect{\bregmanconj(\mu^*; \MAPm)} 
	&\leq \expect{\frac{\mu^*}{\MAPm}}  + \expect{\frac{\MAPm}{\mu^*}} - 1 \\
	&\leq \frac{\mu^*}{\mu_n - \frac{2 \mu^*}{n + n_0}}   + \frac{\mu_n}{\mu^*} - 1 \\
	&= \frac{n_0 + n}{a +n - 2} + \frac{a+n}{n_0 + n} - 2 \\
	&= \frac{n_0 - a + 2}{a +n - 2} + \frac{a - n_0}{n_0 + n} \\
	&= \frac{2}{a+n-2} + \frac{(n_0 - a)^2}{(a+n-2)(n_0 + n)} \\
	\implies \expect{\bregmanconj(\mu^*; \MAPm)} 
	&\leq \frac{1}{a+n-2} + \frac{(n_0 - a)^2}{2(a+n-2)(n_0 + n)} \\
	&\leq \frac{1}{a+n-2} + \frac{\half(1 - \frac{\mu_0}{\mu^*})^2}{(\frac{\mu_0}{\mu^*}+\frac{n-2}{n_0})(1 + \frac{n}{n_0} )} 
\end{align}
where recall that $a=n_0\frac{\mu_0}{\mu^*}$. 
This inequality highlights a clear variance-bias decomposition, to compare with the MLE. Unfortunately it is not tight asymptotically as the inequality \eqref{eq:log_bound} is not quadratically tight around $1$. We are basically losing a factor 2 compared to $1/2n$. by~\eqref{eq:log_bound}.
\end{proof}
